**The status of the microbial census: an update**

### 2015-12-04 doc/notebook/Archaeal_data_acquisition.Rmd
Fix screen.seqs settings and clean up taxonomy

```{r screen_data, engine="bash"}
mothur "#set.current(processors=8);
        screen.seqs(fasta=archaea.fasta, taxonomy=archaea.tax, start=3000, end=7800, maxambig=2, maxhomop=8, minlength=900, inputdir=data/mothur/, outputdir=data/mothur/);"
```

@@

```{r single_cell, engine="bash"}
mothur "#set.dir(input=data/mothur, output=data/mothur);
        align.seqs(fasta=single_cell.archaea.fasta, reference=archaea.good.fasta);
        screen.seqs(fasta=current, start=3000, end=7800, maxambig=2, maxhomop=8, minlength=900);
        classify.seqs(fasta=current, reference=archaea.good.fasta, taxonomy=archaea.good.tax, cutoff=80, processors=8)"
```

@@

```{r process_emirge, engine="bash"}
mothur "#set.dir(input=data/mothur, output=data/mothur);
        align.seqs(fasta=data/mothur/emirge.archaea.fasta, reference=data/mothur/archaea.good.fasta);
        screen.seqs(fasta=current, start=3000, end=7800, maxambig=2, maxhomop=8, minlength=900);
        classify.seqs(fasta=current, reference=data/mothur/archaea.good.fasta, taxonomy=data/mothur/archaea.good.tax, cutoff=80, processors=8)"
```

@@

@@

```{r pool_data, engine="bash"}
cat data/mothur/archaea.good.fasta data/mothur/single_cell.archaea.good.align data/mothur/emirge.archaea.align > data/mothur/all_archaea.align
cat data/mothur/archaea.good.tax data/mothur/single_cell.archaea.good.good.wang.taxonomy data/mothur/emirge.archaea.good.good.wang.taxonomy > data/mothur/all_archaea.taxonomy

mothur "#set.dir(input=data/mothur, output=data/mothur);
        filter.seqs(fasta=all_archaea.align, vertical=T, trump=.);
        unique.seqs();
        pre.cluster(fasta=current, name=current, diffs=9);"

@@

>>>>

```{r screen_data, engine="bash"}
mothur "#screen.seqs(fasta=data/mothur/archaea.fasta, taxonomy=data/mothur/archaea.tax, start=3000, end=7800, maxambig=2, maxhomop=8, processors=8);"
```

@@

```{r single_cell, engine="bash"}
mothur "#set.dir(input=data/mothur, output=data/mothur);
        align.seqs(fasta=single_cell.archaea.fasta, reference=archaea.good.fasta);
        screen.seqs(fasta=current, start=3000, end=7800, maxambig=2, maxhomop=8);
        classify.seqs(fasta=current, reference=archaea.good.fasta, taxonomy=archaea.good.tax, cutoff=80)"
```

@@

```{r process_emirge, engine="bash"}
mothur "#set.dir(input=data/mothur, output=data/mothur);
        align.seqs(fasta=emirge.archaea.fasta, reference=archaea.good.fasta);
        screen.seqs(fasta=current, start=3000, end=7800, maxambig=2, maxhomop=8);
        classify.seqs(fasta=current, reference=archaea.good.fasta, taxonomy=archaea.good.tax, cutoff=80)"
```

@@

Before we can press on with clustering, we need to clean up the taxonomy files that we generated for the EMIRGE and single cell data a bit. We'll do this with R

```{r tax_clean}
tax_clean <- function(tax_file, out_file){
	tax <- scan(file=tax_file, sep='\n', what="", quiet=T)
	tax_clean <- gsub("\\(\\d*\\);", ";", tax)
	tax_clean <- gsub("unclassified;", "", tax_clean)
	write(tax_clean, file=out_file)
}

tax_clean('data/mothur/single_cell.archaea.good.good.wang.taxonomy', 'data/mothur/single_cell.archaea.taxonomy')

tax_clean('data/mothur/emirge.archaea.good.good.wang.taxonomy', 'data/mothur/emirge.archaea.taxonomy')
```

@@

```{r pool_data, engine="bash"}
cat data/mothur/archaea.good.fasta data/mothur/single_cell.archaea.good.align data/mothur/emirge.archaea.good.align > data/mothur/all_archaea.align
cat data/mothur/archaea.good.tax data/mothur/single_cell.archaea.taxonomy data/mothur/emirge.archaea.taxonomy > data/mothur/all_archaea.taxonomy

mothur "#set.dir(input=data/mothur, output=data/mothur);
        filter.seqs(fasta=all_archaea.align, vertical=T, trump=.);
        unique.seqs();
        pre.cluster(fasta=current, name=current, diffs=5);"

@@

XXXXXXXXXXXXXXXX

### 2015-12-04 doc/notebook/Bacterial_data_acquisition.Rmd
Fix screen.seqs settings and clean up taxonomy

```{r screen_data, engine="bash"}
mothur "#screen.seqs(fasta=data/mothur/bacteria.fasta, taxonomy=data/mothur/bacteria.tax, start=2000, end=14459, maxambig=2, minlength=1200, outputdir=data/mothur/, processors=8);"
```

@@

```{r single_cell, engine="bash"}
mothur "#set.dir(output=data/mothur);
        align.seqs(fasta=data/mothur/single_cell.bacteria.fasta, reference=data/mothur/bacteria.good.fasta);
        set.dir(input=data/mothur);
        screen.seqs(fasta=current, start=2000, end=14459, maxambig=2, minlength=1200);
        classify.seqs(fasta=current, reference=data/mothur/bacteria.good.fasta, taxonomy=data/mothur/bacteria.good.tax, cutoff=80)"
```

@@

```{r process_emirge, engine="bash"}
mothur "#set.dir(input=data/mothur, output=data/mothur);
        align.seqs(fasta=data/mothur/emirge.bacteria.fasta, reference=data/references/bacteria.seed.fasta);
        screen.seqs(fasta=current, start=2000, end=14459, maxambig=2, minlength=1200);
        classify.seqs(fasta=current, reference=data/mothur/bacteria.good.fasta, taxonomy=data/mothur/bacteria.good.tax, cutoff=80, processors=8)"
```

@@

@@

```{r pool_data, engine="bash"}
cat data/mothur/bacteria.good.fasta data/mothur/single_cell.bacteria.good.align data/mothur/emirge.bacteria.good.align > data/mothur/all_bacteria.align
cat data/mothur/bacteria.good.tax data/mothur/single_cell.bacteria.good.good.wang.taxonomy data/mothur/emirge.bacteria.good.good.wang.taxonomy > data/mothur/all_bacteria.taxonomy

>>>>

```{r screen_data, engine="bash"}
mothur "#screen.seqs(fasta=data/mothur/bacteria.fasta, taxonomy=data/mothur/bacteria.tax, start=2000, end=14459, maxambig=2, maxhomop=8, outputdir=data/mothur/, processors=8);"
```

@@

```{r single_cell, engine="bash"}
mothur "#set.dir(output=data/mothur);
        align.seqs(fasta=data/mothur/single_cell.bacteria.fasta, reference=data/mothur/bacteria.good.fasta);
        set.dir(input=data/mothur);
        screen.seqs(fasta=current, start=2000, end=14459, maxambig=2);
        classify.seqs(fasta=current, reference=data/mothur/bacteria.good.fasta, taxonomy=data/mothur/bacteria.good.tax, cutoff=80)"
```

@@

```{r process_emirge, engine="bash"}
mothur "#set.dir(input=data/mothur, output=data/mothur);
        align.seqs(fasta=data/mothur/emirge.bacteria.fasta, reference=data/references/bacteria.seed.fasta);
        screen.seqs(fasta=current, start=2000, end=14459, maxambig=2);
        classify.seqs(fasta=current, reference=data/mothur/bacteria.good.fasta, taxonomy=data/mothur/bacteria.good.tax, cutoff=80, processors=8)"
```

@@

Before we can press on with clustering, we need to clean up the taxonomy files that we generated for the EMIRGE and single cell data a bit. We'll do this with R

```{r tax_clean}
tax_clean <- function(tax_file, out_file){
	tax <- scan(file=tax_file, sep='\n', what="", quiet=T)
	tax_clean <- gsub("\\(\\d*\\);", ";", tax)
	tax_clean <- gsub("unclassified;", "", tax_clean)
	write(tax_clean, file=out_file)
}

tax_clean('data/mothur/single_cell.bacteria.good.good.wang.taxonomy', 'data/mothur/single_cell.bacteria.taxonomy')

tax_clean('data/mothur/emirge.bacteria.good.good.wang.taxonomy', 'data/mothur/emirge.bacteria.taxonomy')
```

@@

```{r pool_data, engine="bash"}
cat data/mothur/bacteria.good.fasta data/mothur/single_cell.bacteria.good.align data/mothur/emirge.bacteria.good.align > data/mothur/all_bacteria.align
cat data/mothur/bacteria.good.tax data/mothur/single_cell.bacteria.taxonomy data/mothur/emirge.bacteria.taxonomy > data/mothur/all_bacteria.taxonomy
